Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-02-15 paper.tex
Add todo
add todo
Explain discrepancy in predicted and observed growth rates

@@

@@

Table~\ref{tab:kink_fluting_params} summarises the quantitative differences
between the results for the two values of the resistivity $\eta$ and two models
of viscosity. \rev{The mean across the radius of the ideal estimate of the
growth rate~\eqref{eq:fluting_growth_rate2} provides the theoretical average
growth rate, which is in decent agreement with the observed rate in each case,
particularly in the more ideal case where $\eta=10^{-4}$. \todo{explain discrepancy} The location of the
peak growth rate provides a prediction of where the instability will initially
grow. This radius is used in conjunction with the resonance
equation~\eqref{eq:resonant_surface} (with $m=4$) to predict the axial
wavenumber of the perturbation with the greatest linear growth, i.e. the
perturbation most likely to be observed. Again, these are in good agreement
with the observed fluting wavenumbers, which are measured at times just prior
to the accelerated development of the flute instability, that is at $t=22$ when
$\eta=10^{-3}$ and $t=26$ when $\eta = 10^{-4}$. The kink wavenumber is
measured at $t=26$ in both cases. Overall, the agreement between predicted and observed growth rates and perturbation wavenumbers allows us to conclude that the observed instability is the ideal flute instability and that the growth rate~\eqref{eq:fluting_growth_rate2} can be effectively applied to the instability within coronal loops.}

>>>>

\todo{change u_r to u_x in kink perturbation plot}

@@

\todo{put Q_... in angle brackets and explain what it means in caption}

@@

Table~\ref{tab:kink_fluting_params} summarises the quantitative differences
between the results for the two values of the resistivity $\eta$ and two models
of viscosity. \rev{The mean across the radius of the ideal estimate of the
growth rate~\eqref{eq:fluting_growth_rate2} provides the theoretical average
growth rate, which is in decent agreement with the observed rate in each case,
particularly in the more ideal case where $\eta=10^{-4}$. \rev{The discrepancy between predicted and observed growth rates is due to, in part, the growth rate estimate~\eqref{eq:fluting_growth_rate2} being derived under the assumption $m \gg 1$, which is not true for the observed perturbation where $m=4$. Despite this, the predicted growth rate remains of a similar order of magnitude to the observed rate.} The location of the
peak growth rate provides a prediction of where the instability will initially
grow. This radius is used in conjunction with the resonance
equation~\eqref{eq:resonant_surface} (with $m=4$) to predict the axial
wavenumber of the perturbation with the greatest linear growth, i.e. the
perturbation most likely to be observed. Again, these are in good agreement
with the observed fluting wavenumbers, which are measured at times just prior
to the accelerated development of the flute instability, that is at $t=22$ when
$\eta=10^{-3}$ and $t=26$ when $\eta = 10^{-4}$. The kink wavenumber is
measured at $t=26$ in both cases. Overall, the agreement between predicted and observed growth rates and perturbation wavenumbers allows us to conclude that the observed instability is the ideal flute instability and that the growth rate~\eqref{eq:fluting_growth_rate2} can be effectively applied to the instability within coronal loops.}
